---
output: html_document
---
Reproducible Researh: Course Assignment 1
=========================================

##1.Read and pre-process data
```{r echo=TRUE} 
setwd("C:/Users/Peter/Documents/Coursera/JH_DS/Reproducable Research/Week2/repdata_data_activity")
activity <- read.csv("activity.csv", sep = ",")
activity_rm<-activity[which(!is.na(activity$steps)),] 
```

##2.Histogram of the total number of steps taken each day
```{r echo=TRUE}
perday<-tapply(activity_rm$steps, activity_rm$date, sum) 
hist(perday,10, main = "Total number of steps taken per day", xlab = "") 
```

##3.Mean and median number of steps taken each day
```{r echo=TRUE}
summary(perday)
```

##4.Time series plot of the average number of steps taken
```{r echo=TRUE}
dailyact<-tapply(activity_rm$steps, activity_rm$interval, mean) 
plot(y = dailyact, x = names(dailyact), type = "l", xlab = "5-Minute-Interval", main = "Daily Activity Pattern", ylab = "Average number of steps") 
```

##5.The 5-minute interval that, on average, contains the maximum number of steps
```{r echo=TRUE}
dailyact[dailyact==max(dailyact)]  
```

##6.Code to describe and show a strategy for imputing missing data
```{r echo=TRUE}
act_new <- activity 
act_new[which(is.na(act_new$steps)),1]<- dailyact[as.character(act_new[which(is.na(act_new$steps)),3])] 
```

##7.Histogram of the total number of steps taken each day after missing values are imputed
```{r echo=TRUE}
perday_new<-tapply(act_new$steps, act_new$date, sum) 

hist(perday_new,10, main = "Total number of steps taken per day (missing values imputed)", xlab = "Steps", ylim =c(0, 25)) 
abline(v = median(perday_new), col = 4, lwd = 4) 
```

